Validation of Visual Statistical Inference, with Application to Linear Models

### 2012-04-17 paper_jasa.tex
distribution of p-value

Now suppose $F_{|t|}(.;\delta)$ denotes the distribution function of an absolute value of $t$ distribution with non-centrality parameter $\delta$. Thus the distribution function of $p-value$ be  
\begin{eqnarray}\label{dist_p}
F{p_D}(p) &=& Pr(p_D \le p)=1-Pr(1-p_D \le 1-p) \nonumber \\
  &=& 1-Pr(F_{|t|}^{-1}(1-p_D) \le F_{|t|}^{-1}(1-p) ) \nonumber \\
  &=& 1-Pr(|t_{obs}| \le F_{|t|}^{-1}(1-p)) \nonumber \\
  &=&\left\{ \begin{array}{ll}
          1-F_{|t|}( F_{|t|}^{-1}(1-p))=p &\mbox{ ; under $H_0$} \\
          1-F_{|t|}( F_{|t|}^{-1}(1-p); \delta) &\mbox{ ; under $H_1$} 
       \end{array} \right.     
\end{eqnarray}

Thus the density of $p_D$ is Uniform(0,1)  under $H_0$. As noted by \cite{Ruppert:2007}, under $H_1$ the density $$f_{p_D}(p_D; \delta)= \frac{f_{|t|}(F_{|t|}^{-1}(1-p_D);\delta)}{f_{|t|}(F_{|t|}^{-1}(1-p_D))}$$ derived from equation \ref{dist_p}  is a right skewed distribution.

\blue{Similarly, we will assume that $p_{0,i}$, $i=1, ..., m-1$ are the $p$-values associated with data corresponding to the $m-1$ null plots. Since this data is generated consistently with the null hypothesis, the $p$-values follow a standard Uniform distribution, $p_{i,0} \sim U[0,1], i= 1, ..., m-1$. }

>>>>

Now suppose $F_{|t|}(.;\delta)$ denotes the distribution function of an absolute value of $t$, the classical test statistic, with non-centrality parameter $\delta$. Thus the distribution function of $p-value$ be  
\begin{eqnarray}\label{dist_p}
F{p_D}(p) &=& Pr(p_D \le p)=1-Pr(1-p_D \le 1-p) \nonumber \\
  &=& 1-Pr(F_{|t|}^{-1}(1-p_D) \le F_{|t|}^{-1}(1-p) ) \nonumber \\
  &=& 1-Pr(|t_{obs}| \le F_{|t|}^{-1}(1-p)) \nonumber \\
  &=&\left\{ \begin{array}{ll}
          1-F_{|t|}( F_{|t|}^{-1}(1-p))=p &\mbox{ ; under $H_0$} \\
          1-F_{|t|}( F_{|t|}^{-1}(1-p); \delta) &\mbox{ ; under $H_1$} 
       \end{array} \right.     
\end{eqnarray}

Thus the density of $p_D$ is Uniform(0,1)  under $H_0$. As noted by \cite{Ruppert:2007}, under $H_1$ the density of $p_D$ $$f_{p_D}(p_D; \delta)= \frac{f_{|t|}(F_{|t|}^{-1}(1-p_D);\delta)}{f_{|t|}(F_{|t|}^{-1}(1-p_D))}$$ derived from equation \ref{dist_p}  is a right skewed distribution.

\blue{Similarly, we will assume that $p_{0,i}$, $i=1, ..., m-1$ are the $p$-values associated with data corresponding to the $m-1$ null plots. Since this data is generated consistently with the null hypothesis, by equation \ref{dist_p}, the $p$-values follow a standard Uniform distribution, $p_{i,0} \sim U[0,1], i= 1, ..., m-1$. }
